---
name: Eli D.
surname: Halbreich
position: "Research Assistant, Tufts University"
address: "Department of Psychology,\\tabularnewline 490 Boston Avenue, Medford, MA 02155"
phone: +1 (818) 297-9925
www: elihalbreich.rbind.io
email: "Eli.Halbreich@tufts.edu"
twitter: EliHalbreich
orcid: "0000-0003-4942-9804"
# github: EliHalbreich
date: "`r format(Sys.time(), '%B %Y')`"
output: vitae::hyndman
header-includes:
  \definecolor{headcolor}{HTML}{3E8EDE}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(vitae);library(tibble)
```

# Education

```{r}
tribble(
  ~ Degree,
  ~ Advisor,
  ~ Year,
  ~ Where,
  ~ Institution,
  "Incoming PhD Student, Clinical Psychology",
  "Advisor: Jason Van Allen, PhD",
  "Aug. 2022--2028",
  "Lubbock, TX",
  "Texas Tech University",
  
  "Bachelor of Arts, Psychology",
  "Relevant Coursework: Experimental Psych, Human-Animal Interaction, Clinical Methods, One Health, Statistics for Behavioral Science, The Science of Coping, Abnormal Psych, Black Psych, Personal & Social Development, Seminar in CBT, Social Psych, Understanding Child Development Through Film, Introduction to Cognitive and Brain Sciences",
  "2019--May 2022",
  "Medford, MA",
  "Tufts University, GPA: 4.0",
  "Bachelor of Arts, Psychology",
  "Honors Thesis (2021): Perceived Attitudes of Pet Owners About Their Pets During the COVID-19 Pandemic. Tufts University. Digital Collections and Archives. https://dl.tufts.edu/concern/pdfs/6q183150s",
  "2019--May 2022",
  "Medford, MA",
  "Tufts University, GPA: 4.0",
  
  "Psychology Major",
  "Relevant Coursework: Life-Span Psych, Statistics, Biological Psych, Child Growth and Development, General Psych, Civil Rights and the Law",
  "2017--2019",
  "Los Angeles, CA",
  "Los Angeles City College, GPA: 4.0",
) %>%
  detailed_entries(
    what = Degree,
    when = Year,
    with = Where,
    where = Institution,
    why = Advisor
  )
```

# Honors and Awards

```{r}
tribble(
  ~Year, ~Award, ~Desc,
  "2022--2026", "Helen DeVitt Jones Fellowship", "Texas Tech University Department of Psychological Sciences",
  "2021", "Priscilla N. Dunne Prize", "Tufts University Department of Psychology",
  "2019--2022", "Dean’s List (all full-time semesters)", "Tufts University",
  "2019", "President’s Honors", "Los Angeles City College",
  "2018--2019", "Full Time Dean’s Honor List (all full-time semesters", "Los Angeles City College",
) %>% 
  detailed_entries(
    what = Award,
    when = Year, 
    where = Desc
  )
```

# Publications

\begingroup
\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}
\setlength{\parskip}{8pt}

## Peer-Reviewed Publications

**Halbreich, E. D.** (In Press). Perceived Attitudes of Pet Owners About Their Pets During the COVID-19 Pandemic. *Animalia*.

Mueller, M. K., King, E. K., **Halbreich, E. D.**, & Callina, K. (2022). Pet ownership and adolescent stress and adaptive coping during the COVID-19 Pandemic: Findings from the Adolescent Brain Cognitive Development (ABCD) Study®. *Anthrozoös*. https://doi.org/10.1080/08927936.2022.2027093

**Halbreich, E. D.**, & Mueller, M. K. (2022). Profiles of family pet ownership during the COVID-19 pandemic. *Current Psychology*. https://doi.org/10.1007/s12144-021-02574-x

Linder, D. E., Folta, S. C., Must, A., Mulé, C. M., Cash, S. B., **Halbreich, E. D.**, Colón, C., Sullivan, S., Sanabria, E., Gibbs, D., & Farrell, T. (2021). A stakeholder-engaged approach to development of an animal-assisted intervention for obesity prevention among youth with autism spectrum disorder and their pet dogs. *Frontiers in Veterinary Science*, *8*, 735432. https://doi.org/10.3389/fvets.2021.735432

Linder D. E., Santiago S., & **Halbreich, E. D.** (2021). Is there a correlation between dog obesity and human obesity? Preliminary findings of overweight status among dog owners and their dogs. *Frontiers in Veterinary Science*, *8*, 654617. https://doi.org/10.3389/fvets.2021.654617

## Online Publications

Linder, D. E., & **Halbreich, E. D.** (2022, February 22). *Does My Pet Need a ‘Bland Diet’?* Petfoodology. https://vetnutrition.tufts.edu/2022/02/does-my-pet-need-a-bland-diet/

**Halbreich, E. D.** (2019, December 9). *Tenure Most Foul*. Tufts University Student Scholarship. Tisch Library. http://hdl.handle.net/10427/6W924Q81F

\endgroup  


# Presentations

\begingroup
\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}
\setlength{\parskip}{8pt}

## Poster Presentations

**Halbreich, E. D.** (2022, July 7–9). *Perceived attitudes of pet owners about their pets during the COVID-19 pandemic*. 31st International Society for Anthrozoology Conference, Boise, ID, United States.

Folta, S. C., Mulé, C. M., Linder, D. E., Must, A., Cash, S. B., Adkins, J., & **Halbreich, E. D.** (2022, May 11–14). *Exploring nutrition, physical activity, and the role of pet dogs in households with a child with autism spectrum disorder: The DANE Study*. INSAR 2022 Annual Meeting, Austin, TX, United States.

\endgroup  


# Teaching and Advising

```{r}
tribble(
  ~ Course,
  ~ Instructor,
  ~ Semester,
  ~ Department,
  "Teaching Assistant, Understanding Child Development Through Film",
  "Instructor: Calvin Gidney, PhD",
  "Fall 2020",
  "Tufts University, Eliot-Pearson Department of Child Study and Human Development",
  
    "Teaching Assistant, One Health",
  "Instructor: Deborah Linder, DVM, MS, DACVN",
  "Fall 2020",
  "Tufts University, Department of Community Health",
) %>%
  detailed_entries(
    what = Course,
    when = Semester,
    where = Department,
    why = Instructor
  )
```

# Research Experience
```{r}
tribble(
  ~ Role,
  ~ Research,
  ~ Year,
  ~ Supervisor,
  "Research Assistant, Examining Nutrition, Exercise, and Rest in Growing Youth (ENERGY) Lab",
  "Research Experience: To be determined.",
  "Starting Aug. 2022",
  "Supervisor: Jason Van Allen, PhD",
  
  "Research Coordinator, Children's Television Project",
  "Research Experience: Supervise coders and research assistants working on a longitudinal research project; Work with PIs to implement and improve upon long-term project goals; Organize and manage data from the current season as well as from past years; Assign and track generation of character sheets, coding, cleaning, and collapsing; Generate and manage coder information surveys, training surveys, and coding instrument responses; Respond to student inquiries in a timely manner; and Assist in organizing structure of weekly class meetings as well as semester-long schedule.",
  "2021--May 2022",
  "Supervisor: Calvin Gidney, PhD",
  
    "Research Assistant, Tufts Pets and Well-Being Lab",
  "Research Experience: Work closely with research team on funded research projects; Assist with participant recruitment, consent, protocol training, data collection, debriefing, and tracking; Draft manuscripts and grant proposals; Conduct systematic literature reviews and analyses; Handle data entry and analysis; and Assist with administrative tasks.",
  "May 2021--Aug. 2022",
  "Supervisor: Megan K. Mueller, PhD",
  
    "Research Assistant, Tufts Institute for Human-Animal Interaction",
  "Research Experience: Draft manuscripts; Conduct qualitative interviews with participants; Provide general administrative assistance on a number of funded research projects; Work with the Tufts IRB to help ensure that all aspects of the research studies are in compliance with the applicable regulations and institutional guidelines prior to IRB approval; Facilitate feedback on key documents and managing a collaborative workspace with stakeholders; Oversee projects through varying phases of development; Prepare, draft, and finalize stakeholder and research group meeting agendas and minutes; and Draft and finalize site and study documents.",
  "Aug. 2019--Aug. 2022",
  "Supervisor: Deborah Linder, DVM, MS, DACVN",
) %>%
  detailed_entries(
    what = Role,
    when = Year,
    why = Research,
    where = Supervisor
  )
```

# Professional Society Affiliations

* Psi Chi, The International Honor Society in Psychology
* International Society for Anthrozoology
* American Psychological Association
* American Psychological Association, Division 17, Section 13: The Section on Human-Animal Interaction: Research and Practice
* Human Animal Bond Association
  
# Professional and Departmental Service

```{r}
tribble(
  ~Year, ~Organization, ~Desc,
  "2021--Present", "American Psychological Association", "APA Campus Ambassador",
) %>% 
  detailed_entries(
    what = Desc,
    when = Year, 
    where = Organization
  )
```
  
# Skills

* **Technical**: R, SPSS, REDCap, Qualtrics, Adobe Acrobat, Microsoft Office
* **Language**: English--Native; German--Intermediate High (ACTFL); Spanish--Novice Mid (ACTFL)