---
name: Eli D.
surname: Halbreich
position: "Ph.D. Student, Texas Tech University\\tabularnewline Pronouns: he/him/his"
address: "Department of Psychological Sciences\\tabularnewline Box 42051, Lubbock, TX 79409-2051"
# phone: +1 (818) 297-9925
www: elihalbreich.rbind.io
email: "EliHalbreich@proton.me"
twitter: EliHalbreich
orcid: "0000-0003-4942-9804"
github: EliHalbreich
date: "`r format(Sys.time(), '%B %Y')`"
output: vitae::hyndman
header-includes:
  \definecolor{headcolor}{HTML}{000000}
  \hypersetup{colorlinks=true, linkcolor=blue, filecolor=blue, urlcolor=blue, urlbordercolor=blue}
urlcolor: blue
linkcolor: blue

---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(vitae);library(tibble)
```

# Education

```{r}
tribble(
  ~ Degree,
  ~ Advisor,
  ~ Year,
  ~ Where,
  ~ Institution,
  "Ph.D. Student, Clinical Psychology",
  "Advisor: Jason Van Allen, Ph.D.",
  "2022--2028",
  "Lubbock, TX",
  "Texas Tech University",
  "Ph.D. Student, Clinical Psychology",#this line needs to be the same as above to have the additional bullet below coursework
  "Relevant Coursework: Experimental Design, Practicum in Intelligence Testing, Seminar in Cognition \\& Cognitive Neuroscience, Seminar in Psychopathology, Intro to Clinical Psychology and CBT, Advanced Correlational Methods and Factor Analysis, Lifespan Development, Research Seminar in Clinical and Counseling Psychology, Colloquium in the Teaching of Psychology, Seminar in Professional Ethics, Objective Personality Assessment, Introduction to Psychotherapeutic Intervention and Management, Developmental Psychopathology, Introduction to Child and Adolescent Psychological Treatment, Biological Bases of Psychological Function,  Structural Equation Modeling for Psychologists",#this line needs to be the same as above to have the additional bullet below coursework
  "2022--2028",#this line needs to be the same as above to have the additional bullet below coursework
  "Lubbock, TX",#this line needs to be the same as above to have the additional bullet below coursework
  "Texas Tech University",#this line needs to be the same as above to have the additional bullet below coursework
  "Ph.D. Student, Clinical Psychology",#this line needs to be the same as above to have the additional bullet below coursework
  "Master's Thesis (2024): Pet Ownership and Family Involvement in Sports and Other Activities",#this line needs to be the same as above to have the additional bullet below coursework
  "2022--2028",#this line needs to be the same as above to have the additional bullet below coursework
  "Lubbock, TX",#this line needs to be the same as above to have the additional bullet below coursework
  "Texas Tech University",#this line needs to be the same as above to have the additional bullet below coursework
  
  "Bachelor of Arts, Psychology",
  "Relevant Coursework: Experimental Psych, Human-Animal Interaction, Clinical Methods, One Health, Statistics for Behavioral Science, The Science of Coping, Abnormal Psych, Black Psych, Personal \\& Social Development, Seminar in CBT, Social Psych, Understanding Child Development Through Film, Introduction to Cognitive and Brain Sciences",
  "2019--2022",
  "Medford, MA",
  "Tufts University, \\textit{summa cum laude}, Highest Thesis Honors",
  "Bachelor of Arts, Psychology",#this line needs to be the same as above to have the additional bullet below coursework
  "Honors Thesis (2021): Perceived Attitudes of Pet Owners About Their Pets During the COVID-19 Pandemic. Tufts University. Digital Collections and Archives. \\textcolor{blue}{https://dl.tufts.edu/concern/pdfs/6q183150s}",
  "2019--2022",#this line needs to be the same as above to have the additional bullet below coursework
  "Medford, MA",#this line needs to be the same as above to have the additional bullet below coursework
  "Tufts University, \\textit{summa cum laude}, Highest Thesis Honors",#this line needs to be the same as above to have the additional bullet below coursework
  
  "Psychology Major",
  "Relevant Coursework: Life-Span Psych, Statistics, Biological Psych, Child Growth and Development, General Psych, Civil Rights and the Law",
  "2017--2019",
  "Los Angeles, CA",
  "Los Angeles City College",
) %>%
  detailed_entries(
    what = Degree,
    when = Year,
    with = Where,
    where = Institution,
    why = Advisor,
    .protect = FALSE
  )
```

# Grants and Fellowships

```{r}
tribble(
  ~ Year,
  ~ Award,
  ~ Amount,
  ~ Institution,
  "2023", "2023 APAGS/Psi Chi Junior Scientist Fellowship","Amount: \\$1,000","American Psychological Association of Graduate Students \\& Psi Chi",
  "2022--2026", "Helen DeVitt Jones Fellowship","Amount: \\$16,000","Texas Tech University Department of Psychological Sciences",
) %>%
  detailed_entries(
    what = Award,
    when = Year,
    with = Amount,
    where = Institution,
    .protect = FALSE
  )
```

# Honors and Awards

```{r}
tribble(
  ~Year, ~Award, ~Desc, ~Amount,
  "2021", "Priscilla N. Dunne Prize", "Tufts University Department of Psychology","Amount: \\$1,000",
  "2021", "TIHAI Student Scholar", "Tufts Initiative for Human-Animal Interaction", "Amount: \\$500",
  "2019--2022", "Dean’s List (all full-time semesters)", "Tufts University","",
  "2019", "President’s Honors", "Los Angeles City College","",
  "2018--2019", "Full Time Dean’s Honor List (all full-time semesters)", "Los Angeles City College","",
) %>% 
  detailed_entries(
    what = Award,
    when = Year,
    with = Amount,
    where = Desc,
    .protect = FALSE
  )
```

# Grant and Fellowship Applications

```{r}
tribble(
  ~ Year,
  ~ Award,
  ~ Amount,
  ~ Institution,
  ~ Status,
      "2024",
  "TTU Institute for Studies in Pragmaticism, Cross-Disciplinary Research Excellence Award",
  "Amount: \\$6,000",
  "Title: Examining the impact of animal-assisted therapy on pediatric patients' psychological and physical health (Role: Co-I)",
  "Status: Submitted",
  
  "2023",
  "American Foundation for Suicide Prevention, Pilot Innovation Grant",
  "Amount: \\$49,870",
  "Title: Real-time assessment of suicidal thoughts and behaviors among sexual and gender minority young adults with companion animals (Role: Co-PI)",
  "Status: Submitted",
  
    "2023",
  "National Science Foundation, Graduate Research Fellowship Program",
  "Amount: \\$111,000",
  "Title: Companion animals, social support, and coping in rural and urban LGBTQ+ and non-LGBTQ+ adolescents and young adults (Role: PI)",
  "Status: Not recommended",
  
    "2023",
  "Society of Pediatric Psychology, Marion and Donald Routh Student Research Grant",
  "Amount: \\$5,000",
  "Title: Examining the impact of animal-assisted therapy on pediatric patients' psychological and physical health (Role: Co-I)",
  "Status: Declined by funder",
  
    "2023",
  "American Psychological Foundation, Visionary Grant",
  "Amount: \\$20,000",
  "Title: Real-time assessment of suicidal thoughts and behaviors among sexual and gender minority young adults with companion animals (Role: Co-PI)",
  "Status: Declined by funder",
  
    "2023",
  "Human Animal Bond Research Institute, 2023 Proposal",
  "Amount: \\$49,500",
  "Title: Companion animals, social support, and coping in rural and urban LGBTQ+ and non-LGBTQ+ adolescents and young adults (Role: Co-I)",
  "Status: Declined by funder",
  
  "2022",
  "University of North Texas Center for Psychosocial Health Disparities Research, Improving Behavioral Health of Underserved Groups",
  "Amount: \\$10,000",
  "Title: Companion animals, social support, and coping in rural LGBT+ youth (Role: PI)",
  "Status: Declined by funder",

) %>%
  detailed_entries(
    what = Award,
    when = Year,
    with = Amount,
    where = Institution,
    why = Status,
    .protect = FALSE
  )
```

# Publications

*Indicates undergraduate trainee author/presenter

\begingroup
\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}
\setlength{\parskip}{8pt}

[Google Scholar Profile](https://scholar.google.com/citations?user=ffVvNRYAAAAJ)

## Peer-Reviewed Publications

King, E. K., **Halbreich, E. D.**, Callina, K., & Mueller, M. K. (2023). Companion animals and the relationship between peer victimization and emotion regulation in youth. *Journal of Research on Adolescence*, *34*(1), 85--95. https://doi.org/10.1111/jora.12901

Mueller, M. K., King, E. K., **Halbreich, E. D.**, & Anderson, E. (2023) Feasibility of using ecological momentary assessment to measure the effects of interactions with pet dogs on psychophysiological reactivity in adolescents with social anxiety. *Human-Animal Interactions*, *11*(1), https://doi.org/10.1079/hai.2023.0036

**Halbreich, E. D.**, Callina, K., King, E. K., & Mueller, M. K. (2023). Companion animals and profiles of peer social behavior in adolescence. *Journal of Adolescence*, *95*(6), 1152--1167. https://doi.org/10.1002/jad.12183

**Halbreich, E. D.** (2022). Perceived attitudes of pet owners about their pets during the COVID-19 pandemic. *Animalia: An Anthrozoology Journal*, *6*(1), 1--13. https://www.animaliajournal.org/post/perceived-attitudes-of-pet-owners-about-their-pets-during-the-covid-19-pandemic

Mueller, M. K., King, E. K., **Halbreich, E. D.**, & Callina, K. S. (2022). Companion animals and adolescent stress and adaptive coping during the COVID-19 pandemic. *Anthrozoös*, *35*(5), 693--712. https://doi.org/10.1080/08927936.2022.2027093

**Halbreich, E. D.**, & Mueller, M. K. (2022). Profiles of family pet ownership during the COVID-19 pandemic. *Current Psychology*. https://doi.org/10.1007/s12144-021-02574-x

Linder, D. E., Folta, S. C., Must, A., Mulé, C. M., Cash, S. B., **Halbreich, E. D.**, Colón, C., Sullivan, S., Sanabria, E., Gibbs, D., & Farrell, T. (2021). A stakeholder-engaged approach to development of an animal-assisted intervention for obesity prevention among youth with autism spectrum disorder and their pet dogs. *Frontiers in Veterinary Science*, *8*, 735432. https://doi.org/10.3389/fvets.2021.735432

Linder D. E., Santiago S., & **Halbreich, E. D.** (2021). Is there a correlation between dog obesity and human obesity? Preliminary findings of overweight status among dog owners and their dogs. *Frontiers in Veterinary Science*, *8*, 654617. https://doi.org/10.3389/fvets.2021.654617

## Book Chapters

King, E. K., **Halbreich, E. D.**, & Mueller, M. K. (2023). Animals in development: Childhood and adolescence. In A. H. Fine, M. K. Mueller, Z. Y. Ng, A. M. Beck, & J. M. Peralta  (Eds.), *The Routledge International Handbook of Human-Animal Interactions and Anthrozoology*. https://doi.org/10.4324/9781032153346

## Online Publications

Linder, D. E., & **Halbreich, E. D.** (2022, February 22). *Does My Pet Need a ‘Bland Diet’?* Petfoodology. https://vetnutrition.tufts.edu/2022/02/does-my-pet-need-a-bland-diet/

**Halbreich, E. D.** (2019, December 9). *Tenure Most Foul*. Tufts University Student Scholarship. Tisch Library. http://hdl.handle.net/10427/6W924Q81F

\endgroup  


# Presentations

\begingroup
\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}
\setlength{\parskip}{8pt}

## Symposium Contributions

Mueller, M. K., **Halbreich, E. D.**, & Anderson, E. (2022, July 7--9). Feasibility of using ecological momentary assessment to measure the effects of interactions with pet dogs on psychophysiological reactivity in adolescents with social anxiety. In N. Gee (Chair), *Ecological Momentary Assessment (EMA) as a Tool for Assessing Human-animal Interaction Across Contexts*. 31st International Society for Anthrozoology Conference, Boise, ID, United States.

## Poster Presentations

**Halbreich, E. D.**, Hefner, T. D., & Van Allen, J. (2024, April 18--20). *Pet ownership and physical activity in adolescence*. The Society for Research on Adolescence 2024 Annual Meeting, Chicago, IL, United States.

King, E. K., **Halbreich, E. D.**, Anderson, E., & Mueller, M. K. (2023, June 15--18). *Dog interactions and psychophysiology in adolescents with social anxiety*. 32nd International Society for Anthrozoology Conference, Edinburgh, Scotland.

\*Streicher, B. E., **Halbreich, E. D.**, Healy, A, Hefner, T. D., Lelakowska, G., & Van Allen, J. (2023, May 3). *Dog ownership, physical activity, depression, and anxiety symptoms in youth*. Obesity Research Institute 8th Annual Meeting, Lubbock, TX, United States.

**Halbreich, E. D.**, Mueller, M. K., King, E. K., & Callina, K. (2023, April 13--15). *Pet ownership and profiles of peer social behavior in adolescence*. The Society for Research on Adolescence 2023 Annual Meeting, San Diego, CA, United States.

**Halbreich, E. D.** (2022, July 7--9). *Perceived attitudes of pet owners about their pets during the COVID-19 pandemic*. 31st International Society for Anthrozoology Conference, Boise, ID, United States.

Folta, S. C., Mulé, C. M., Linder, D. E., Must, A., Cash, S. B., Adkins, J., & **Halbreich, E. D.** (2022, May 11--14). *Exploring nutrition, physical activity, and the role of pet dogs in households with a child with autism spectrum disorder: The DANE Study*. INSAR 2022 Annual Meeting, Austin, TX, United States.

\endgroup  

# Research and Clinical Experience

## Research Experience

```{r}
tribble(
  ~ Role,
  ~ Research,
  ~ Year,
  ~ Supervisor,
  "Research Assistant, Examining Nutrition, Exercise, and Rest in Growing Youth (ENERGY) Lab",
  "Propose and manage new research projects; Write grant applications for relevant funding opportunities; Work collaborative on funded research projects; Supervise undergraduate research assistants on research projects; and Assist with administrative tasks.",
  "Aug. 2022--Present",
  "Supervisor: Jason Van Allen, Ph.D.",
  
  "Research Coordinator, Children's Television Project",
  "Supervise coders and research assistants working on a longitudinal research project; Work with PIs to implement and improve upon long-term project goals; Organize and manage data from the current season as well as from past years; Assign and track generation of character sheets, coding, cleaning, and collapsing; Generate and manage coder information surveys, training surveys, and coding instrument responses; Respond to student inquiries in a timely manner; and Assist in organizing structure of weekly class meetings as well as semester-long schedule.",
  "Aug. 2021--May 2022",
  "Supervisor: Calvin Gidney, Ph.D.",
  
    "Research Assistant, Tufts Pets and Well-Being Lab",
  "Work closely with research team on funded research projects; Assist with participant recruitment, consent, protocol training, data collection, debriefing, and tracking; Draft manuscripts and grant proposals; Conduct systematic literature reviews and analyses; Handle data entry and analysis; and Assist with administrative tasks.",
  "May 2021--Aug. 2022",
  "Supervisor: Megan K. Mueller, Ph.D.",
  
    "Research Assistant, Tufts Initiative for Human-Animal Interaction",
  "Draft manuscripts; Conduct qualitative interviews with participants; Provide general administrative assistance on a number of funded research projects; Work with the Tufts IRB to help ensure that all aspects of the research studies are in compliance with the applicable regulations and institutional guidelines prior to IRB approval; Facilitate feedback on key documents and managing a collaborative workspace with stakeholders; Oversee projects through varying phases of development; Prepare, draft, and finalize stakeholder and research group meeting agendas and minutes; and Draft and finalize site and study documents.",
  "Aug. 2019--Aug. 2022",
  "Supervisor: Deborah Linder, DVM, MS, DACVN",
) %>%
  detailed_entries(
    what = Role,
    when = Year,
    why = Research,
    where = Supervisor
  )
```

## Clinical Experience

```{r}
tribble(
  ~ Role,
  ~ Research,
  ~ Year,
  ~ Supervisor,
      "Texas Tech University, Texas Tech University Psychology Clinic",
  "Graduate Student | Individual Child Therapist",
  "Jan. 2024--May 2024",
  "Supervisor: John L. Cooley, Ph.D.",
        "Texas Tech University, Texas Tech University Psychology Clinic",
  "Clinical Emphasis: Parent Management Training, Defiant Children,  Trauma-Focused Cognitive Behavioral Therapy",
  "Jan. 2024--May 2024",
  "Supervisor: John L. Cooley, Ph.D.",
  
        "Texas Tech University, Texas Tech University Psychology Clinic",
  "Graduate Student | Individual Adult Therapist",
  "Jan. 2024--May 2024",
  "Supervisor: Sarah E. Victor, Ph.D.",
  
        "Texas Tech University, Grief Therapy with Adolescents",
  "Practicum Student | Group Therapist",
  "Sep. 2023--Aug. 2024",
  "Supervisor: Jonathan Singer, Ph.D.",
          "Texas Tech University, Grief Therapy with Adolescents",
  "Administering Trauma and Grief Component Therapy (TGCT) for adolescents who have lost a family member",
  "Sep. 2023--Aug. 2024",
  "Supervisor: Jonathan Singer, Ph.D.",
  
      "Texas Tech University, CBT Pain Program for Adolescents",
  "Practicum Student | Group Therapist",
  "Sep. 2023--Aug. 2024",
  "Supervisor: Caroline Cummings, Ph.D.",
        "Texas Tech University, CBT Pain Program for Adolescents",
  "Administering a CBT-based pain protocol for adolescents with chronic pain and their parents",
  "Sep. 2023--Aug. 2024",
  "Supervisor: Caroline Cummings, Ph.D.",
  
      "Texas Tech University, Texas Tech University Psychology Clinic",
  "Graduate Student | Individual Adult Therapist",
  "Sep. 2023--Dec. 2023",
  "Supervisor: Andrew Littlefield, Ph.D.",
        "Texas Tech University, Texas Tech University Psychology Clinic",
  "Clinical Emphasis: Motivational Interviewing",
  "Sep. 2023--Dec. 2023",
  "Supervisor: Andrew Littlefield, Ph.D.",
  
    "Texas Tech University, Texas Tech University Psychology Clinic",
  "Clinic Co-Director",
  "Jan. 2023--May 2023",
  "Supervisor: Megan A. Thoen, Ph.D.",
) %>%
  detailed_entries(
    what = Role,
    when = Year,
    why = Research,
    where = Supervisor
  )
```

# Teaching and Mentoring Experience

## Teaching

```{r}
tribble(
  ~ Course,
  ~ Instructor,
  ~ Semester,
  ~ Department,
  "Teaching Assistant, Statistical Methods Lab",
  "Instructor: Will Crescioni, Ph.D.",
  "Fall 2022",
  "Texas Tech University, Department of Psychological Sciences",
  
  "Teaching Assistant, Understanding Child Development Through Film",
  "Instructor: Calvin Gidney, Ph.D.",
  "Fall 2020",
  "Tufts University, Eliot-Pearson Department of Child Study and Human Development",
  
  "Teaching Assistant, One Health",
  "Instructor: Deborah Linder, DVM, MS, DACVN",
  "Fall 2020",
  "Tufts University, Department of Community Health",
) %>%
  detailed_entries(
    what = Course,
    when = Semester,
    where = Department,
    why = Instructor
  )
```

## Mentoring

```{r}
tribble(
  ~ Advisee,
  ~ Instructor,
  ~ Semester,
  "Cyerra Jones",
  "Current mentee",
  "2023--Ongoing",
  "Madeleine Valley",
  "Current mentee",
  "2023--Ongoing",
  "Amanda Tabansi",
  "Current mentee",
  "2023--Ongoing",
  "Macie Le",
  "Undergraduate Research Assistant",
  "2023--2023",
  "Abigail Woodall",
  "Current mentee",
  "2023--Ongoing",
  "Sara Phy",
  "Subsequent Position: Master of Public Health Student, Nutritional Sciences, Dietetics Concentration, University of Michigan",
  "2023",
  "Brooke Streicher",
  "Subsequent Position: Research Coordinator, Texas Tech University",
  "2022--2023",
  "Ellis Renwick-Archibold",
  "Science Research Program, New Rochelle High School",
  "Summer 2022",

) %>%
  detailed_entries(
    what = Advisee,
    when = Semester,
    why = Instructor
  )
```

# Professional Service and Development

```{r}
tribble(
  ~Year, ~Organization, ~Desc,
"May. 2023", "Texas Tech University", "The Groundwork Program",
"Mar. 2023", "Texas Tech University", "Organizing the Academic CV Workshop",
"Feb. 2023", "Texas Tech University", "Writing the Academic Cover Letter Workshop",
"Jan. 2023", "Texas Tech University", "Making Equitable Attendance Policies Workshop",
"2022--2023", "American Psychological Association, Division 17, Section 13: The Section on Human-Animal Interaction: Research and Practice", "Inclusion, Diversity, Equity, and Access (IDEA) Committee Member",
"2022--2023", "American Psychological Association, Division 17, Section 13: The Section on Human-Animal Interaction: Research and Practice", "Student Representative",
  "2021--2023", "American Psychological Association", "APA Campus Ambassador",
) %>% 
  detailed_entries(
    what = Desc,
    when = Year, 
    where = Organization
  )
```
  
# Skills

```{r}
tribble(
  ~Category, ~Desc,
  "Programming & Software:", "R, RStudio, Quarto, Markdown, MPlus, SPSS, MATLAB, REDCap, Qualtrics, LaTeX, Adobe Acrobat, Microsoft Office",
  "Languages:", "English--Native; German--Intermediate High (ACTFL); Spanish--Novice Mid (ACTFL)"
) %>% 
  brief_entries(
    what = Desc,
    when = Category
  )
```

# Certifications

```{r}
tribble(
  ~Year, ~Organization, ~Desc,
  "2 May 2024", "Texas A&M Health Telehealth Institute", "Telehealth 101",
  "9 Nov. 2023", "The Trauma and Grief Center at the Hackett Center for Mental Health", "Multidimensional Grief Therapy (MGT) Overview Training",
  "21 Sep. 2023", "MoCA Cognitive Assessment", "Certified Rater",
  "6 Apr. 2023", "QPR Institute", "QPR Gatekeeper",
  "6 Jan. 2023", "CITI Program", "Working with Dogs in Research Settings",
  "13 Dec. 2022", "CITI Program", "Working With Horses In An Agricultural Research Setting",
  "10 Sep. 2022", "CITI Program", "TTU Human Subject Research Course",
  "9 Sep. 2022", "CITI Program", "Social and Behavioral Responsible Scholarship Course",
) %>% 
  detailed_entries(
    what = Desc,
    when = Year, 
    where = Organization
  )
```

# Professional Society Affiliations  

```{r}
tribble(
  ~Desc,
  "Psi Chi, The International Honor Society in Psychology", "American Psychological Association, Division 53: Society of Clinical Child and Adolescent Psychology", "American Psychological Association, Division 17, Section 13: The Section on Human-Animal Interaction: Research and Practice", "Human Animal Bond Association"
) %>% 
  brief_entries(
    when = Desc
  )
```