---
name: Eli D.
surname: Halbreich, M.A.
position: "Ph.D. Student, Texas Tech University\\tabularnewline Pronouns: he/him/his"
address: "Department of Psychological Sciences\\tabularnewline Box 42051, Lubbock, TX 79409-2051"
# phone: +1 (818) 297-9925
www: elihalbreich.rbind.io
email: "EliHalbreich@proton.me"
twitter: EliHalbreich
orcid: "0000-0003-4942-9804"
github: EliHalbreich
date: "`r format(Sys.time(), '%B %Y')`"
output: vitae::hyndman
header-includes:
  \definecolor{headcolor}{HTML}{000000}
  \hypersetup{colorlinks=true, linkcolor=blue, filecolor=blue, urlcolor=blue, urlbordercolor=blue}
urlcolor: blue
linkcolor: blue

---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(vitae);library(tibble)
```

# Education

```{r}
tribble(
  ~ Degree,
  ~ Advisor,
  ~ Year,
  ~ Where,
  ~ Institution,
  "Doctor of Philosophy, Clinical Psychology (Expected August 2028)",
  "Advisor: Jason Van Allen, Ph.D.",
  "2022--Present",
  "Lubbock, TX",
  "Texas Tech University (APA Accredited)",
  
  "Master of Arts, Clinical Psychology",
  "Advisor: Jason Van Allen, Ph.D.",
  "2022--2024",
  "Lubbock, TX",
  "Texas Tech University (APA Accredited)",
  
  "Master of Arts, Clinical Psychology",#this line needs to be the same as above to have the additional bullet below coursework
  "Master's Thesis (2024): Pet Ownership and Family Involvement in Sports and Other Activities. Texas Tech University. Electronic Theses and Dissertations. \\textcolor{blue}{https://hdl.handle.net/2346/99242}",#this line needs to be the same as above to have the additional bullet below coursework
  "2022--2024",#this line needs to be the same as above to have the additional bullet below coursework
  "Lubbock, TX",#this line needs to be the same as above to have the additional bullet below coursework
  "Texas Tech University (APA Accredited)",#this line needs to be the same as above to have the additional bullet below coursework
  
  "Bachelor of Arts, Psychology",
  "Advisor: Alexander Queen, Ph.D.",
  "2019--2022",
  "Medford, MA",
  "Tufts University, \\textit{summa cum laude}, Highest Thesis Honors",
        "Bachelor of Arts, Psychology",
  "Honors Thesis (2021): Perceived Attitudes of Pet Owners About Their Pets During the COVID-19 Pandemic. Tufts University. Digital Collections and Archives. \\textcolor{blue}{https://dl.tufts.edu/concern/pdfs/6q183150s}",
  "2019--2022",
  "Medford, MA",
  "Tufts University, \\textit{summa cum laude}, Highest Thesis Honors",
  
  "Psychology Major",
  "Advisor: Glenn White, Ph.D.",
  "2017--2019",
  "Los Angeles, CA",
  "Los Angeles City College",
  
) %>%
  detailed_entries(
    what = Degree,
    when = Year,
    with = Where,
    where = Institution,
    why = Advisor,
    .protect = FALSE
  )
```

# Grants and Fellowships

```{r}
tribble(
  ~ Year,
  ~ Award,
  ~ Amount,
  ~ Institution,
  "2023", "2023 APAGS/Psi Chi Junior Scientist Fellowship","Amount: \\$1,000","American Psychological Association of Graduate Students \\& Psi Chi",
  "2022--2026", "Helen DeVitt Jones Fellowship","Amount: \\$16,000","Texas Tech University Department of Psychological Sciences",
) %>%
  detailed_entries(
    what = Award,
    when = Year,
    with = Amount,
    where = Institution,
    .protect = FALSE
  )
```

# Honors and Awards

```{r}
tribble(
  ~Year, ~Award, ~Desc, ~Amount,
  "2021", "Priscilla N. Dunne Prize", "Tufts University Department of Psychology","Amount: \\$1,000",
  "2021", "TIHAI Student Scholar", "Tufts Initiative for Human-Animal Interaction", "Amount: \\$500",
  "2019--2022", "Dean’s List (all full-time semesters)", "Tufts University","",
  "2019", "President’s Honors", "Los Angeles City College","",
  "2018--2019", "Full Time Dean’s Honor List (all full-time semesters)", "Los Angeles City College","",
) %>% 
  detailed_entries(
    what = Award,
    when = Year,
    with = Amount,
    where = Desc,
    .protect = FALSE
  )
```

# Grant and Fellowship Applications

```{r}
tribble(
  ~ Year,
  ~ Award,
  ~ Amount,
  ~ Institution,
  ~ Status,
  
        "2024",
  "TTU Institute for Studies in Pragmaticism, Charles S. Peirce Interdisciplinary Graduate Fellowship",
  "Amount: \\$5,000",
  "Title: Examining the Role of Animal-Assisted Therapy (AAT) with Pediatric Physical Therapy (PT) Patients (Role: Co-PI)",
  "Status: Under review",
  
      "2024",
  "TTU Institute for Studies in Pragmaticism, Cross-Disciplinary Research Excellence Award",
  "Amount: \\$6,000",
  "Title: Examining the impact of animal-assisted therapy on pediatric patients' psychological and physical health (Role: Co-I)",
  "Status: Declined by funder",
  
  "2023",
  "American Foundation for Suicide Prevention, Pilot Innovation Grant",
  "Amount: \\$49,870",
  "Title: Real-time assessment of suicidal thoughts and behaviors among sexual and gender minority young adults with companion animals (Role: Co-PI)",
  "Status: Declined by funder",
  
    "2023",
  "National Science Foundation, Graduate Research Fellowship Program",
  "Amount: \\$111,000",
  "Title: Companion animals, social support, and coping in rural and urban LGBTQ+ and non-LGBTQ+ adolescents and young adults (Role: PI)",
  "Status: Not recommended",
  
    "2023",
  "Society of Pediatric Psychology, Marion and Donald Routh Student Research Grant",
  "Amount: \\$5,000",
  "Title: Examining the impact of animal-assisted therapy on pediatric patients' psychological and physical health (Role: Co-I)",
  "Status: Declined by funder",
  
    "2023",
  "American Psychological Foundation, Visionary Grant",
  "Amount: \\$20,000",
  "Title: Real-time assessment of suicidal thoughts and behaviors among sexual and gender minority young adults with companion animals (Role: Co-PI)",
  "Status: Declined by funder",
  
    "2023",
  "Human Animal Bond Research Institute, 2023 Proposal",
  "Amount: \\$49,500",
  "Title: Companion animals, social support, and coping in rural and urban LGBTQ+ and non-LGBTQ+ adolescents and young adults (Role: Co-I)",
  "Status: Declined by funder",
  
  "2022",
  "University of North Texas Center for Psychosocial Health Disparities Research, Improving Behavioral Health of Underserved Groups",
  "Amount: \\$10,000",
  "Title: Companion animals, social support, and coping in rural LGBT+ youth (Role: PI)",
  "Status: Declined by funder",

) %>%
  detailed_entries(
    what = Award,
    when = Year,
    with = Amount,
    where = Institution,
    why = Status,
    .protect = FALSE
  )
```


# Publications

*Indicates undergraduate trainee author/presenter

\begingroup
\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}
\setlength{\parskip}{8pt}

[Google Scholar Profile](https://scholar.google.com/citations?user=ffVvNRYAAAAJ)

## Peer-Reviewed Publications

**Halbreich, E. D.**, & Van Allen, J. (2024). Pet Ownership and Family Involvement in Sports and Other Activities. *Anthrozoös*, *37*(6), 1107--1131. https://doi.org/10.1080/08927936.2024.2406097

**Halbreich, E. D.**, Hefner, T. D., Healy, A. S., & Van Allen, J. (2024). Measurement of attachment in human-animal interaction research. *Human-Animal Interactions*, *12*(1). https://doi.org/10.1079/hai.2024.0030

King, E. K., **Halbreich, E. D.**, Callina, K., & Mueller, M. K. (2023). Companion animals and the relationship between peer victimization and emotion regulation in youth. *Journal of Research on Adolescence*, *34*(1), 85--95. https://doi.org/10.1111/jora.12901

Mueller, M. K., King, E. K., **Halbreich, E. D.**, & Anderson, E. (2023) Feasibility of using ecological momentary assessment to measure the effects of interactions with pet dogs on psychophysiological reactivity in adolescents with social anxiety. *Human-Animal Interactions*, *11*(1), https://doi.org/10.1079/hai.2023.0036

**Halbreich, E. D.**, Callina, K., King, E. K., & Mueller, M. K. (2023). Companion animals and profiles of peer social behavior in adolescence. *Journal of Adolescence*, *95*(6), 1152--1167. https://doi.org/10.1002/jad.12183

**Halbreich, E. D.** (2022). Perceived attitudes of pet owners about their pets during the COVID-19 pandemic. *Animalia: An Anthrozoology Journal*, *6*(1), 1--13. https://www.animaliajournal.org/post/perceived-attitudes-of-pet-owners-about-their-pets-during-the-covid-19-pandemic

Mueller, M. K., King, E. K., **Halbreich, E. D.**, & Callina, K. S. (2022). Companion animals and adolescent stress and adaptive coping during the COVID-19 pandemic. *Anthrozoös*, *35*(5), 693--712. https://doi.org/10.1080/08927936.2022.2027093

**Halbreich, E. D.**, & Mueller, M. K. (2022). Profiles of family pet ownership during the COVID-19 pandemic. *Current Psychology*. https://doi.org/10.1007/s12144-021-02574-x

Linder, D. E., Folta, S. C., Must, A., Mulé, C. M., Cash, S. B., **Halbreich, E. D.**, Colón, C., Sullivan, S., Sanabria, E., Gibbs, D., & Farrell, T. (2021). A stakeholder-engaged approach to development of an animal-assisted intervention for obesity prevention among youth with autism spectrum disorder and their pet dogs. *Frontiers in Veterinary Science*, *8*, 735432. https://doi.org/10.3389/fvets.2021.735432

Linder D. E., Santiago S., & **Halbreich, E. D.** (2021). Is there a correlation between dog obesity and human obesity? Preliminary findings of overweight status among dog owners and their dogs. *Frontiers in Veterinary Science*, *8*, 654617. https://doi.org/10.3389/fvets.2021.654617

## Book Chapters

King, E. K., **Halbreich, E. D.**, & Mueller, M. K. (2023). Animals in development: Childhood and adolescence. In A. H. Fine, M. K. Mueller, Z. Y. Ng, A. M. Beck, & J. M. Peralta  (Eds.), *The Routledge International Handbook of Human-Animal Interactions and Anthrozoology*. https://doi.org/10.4324/9781032153346

## Online Publications

Linder, D. E., & **Halbreich, E. D.** (2022, February 22). *Does My Pet Need a ‘Bland Diet’?* Petfoodology. https://vetnutrition.tufts.edu/2022/02/does-my-pet-need-a-bland-diet/

**Halbreich, E. D.** (2019, December 9). *Tenure Most Foul*. Tufts University Student Scholarship. Tisch Library. http://hdl.handle.net/10427/6W924Q81F

## Selected Manuscripts in Preparation

Hefner, T. D., **Halbreich, E. D.**, Jones, J., \*Arendt, F., \*Jones, C., & \*Valley, M. (In Prep). Systematic review and meta-analysis of cognitive-dissonance interventions to improve body image satisfaction among athletes.

Lancaster, B. D., Hefner, T. D., **Halbreich, E. D.**, Hall, N. J., & Van Allen, J. (In Prep). The effect of pet dogs on empirical measures of child activity.

**Halbreich, E. D.**, Hefner, T. D., & Van Allen, J. (In Prep). Construction and validation of the companion animal ties scale (CATS).

**Halbreich, E. D.**, & Van Allen, J. (In Prep). Examining the relationship between pet ownership and prosocial behaviors.

\endgroup  

# Presentations

\begingroup
\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}
\setlength{\parskip}{8pt}

## Symposium Contributions

Mueller, M. K., **Halbreich, E. D.**, & Anderson, E. (2022, July 7--9). Feasibility of using ecological momentary assessment to measure the effects of interactions with pet dogs on psychophysiological reactivity in adolescents with social anxiety. In N. Gee (Chair), *Ecological Momentary Assessment (EMA) as a Tool for Assessing Human-animal Interaction Across Contexts*. 31st International Society for Anthrozoology Conference, Boise, ID, United States.

## Poster Presentations

Hefner, T. D., **Halbreich, E. D.**, Jones, C., \*Valley, M., & Van Allen, J. (2025, April 3--5). *Relationship between pet ownership, physical activity, and sleep recommendations*. Society of Pediatric Psychology 2025 Annual Conference, Phoenix, AZ, United States.

**Halbreich, E. D.**, \*Arendt, F., Hefner, T. D., & Van Allen, J. (2025, April 3--5). *Evaluating prosocial behavior and sleep disturbances between pet owners and non-pet owners*. Society of Pediatric Psychology 2025 Annual Conference, Phoenix, AZ, United States.

**Halbreich, E. D.**, Hefner, T. D., & Van Allen, J. (2024, April 18--20). *Pet ownership and physical activity in adolescence*. The Society for Research on Adolescence 2024 Annual Meeting, Chicago, IL, United States.

King, E. K., **Halbreich, E. D.**, Anderson, E., & Mueller, M. K. (2023, June 15--18). *Dog interactions and psychophysiology in adolescents with social anxiety*. 32nd International Society for Anthrozoology Conference, Edinburgh, Scotland.

\*Streicher, B. E., **Halbreich, E. D.**, Healy, A, Hefner, T. D., Lelakowska, G., & Van Allen, J. (2023, May 3). *Dog ownership, physical activity, depression, and anxiety symptoms in youth*. Obesity Research Institute 8th Annual Meeting, Lubbock, TX, United States.

**Halbreich, E. D.**, Mueller, M. K., King, E. K., & Callina, K. (2023, April 13--15). *Pet ownership and profiles of peer social behavior in adolescence*. The Society for Research on Adolescence 2023 Annual Meeting, San Diego, CA, United States.

**Halbreich, E. D.** (2022, July 7--9). *Perceived attitudes of pet owners about their pets during the COVID-19 pandemic*. 31st International Society for Anthrozoology Conference, Boise, ID, United States.

Folta, S. C., Mulé, C. M., Linder, D. E., Must, A., Cash, S. B., Adkins, J., & **Halbreich, E. D.** (2022, May 11--14). *Exploring nutrition, physical activity, and the role of pet dogs in households with a child with autism spectrum disorder: The DANE Study*. INSAR 2022 Annual Meeting, Austin, TX, United States.

\endgroup  

# Research and Clinical Experience

## Research Experience

```{r}
tribble(
  ~ Role,
  ~ Research,
  ~ Year,
  ~ Supervisor,
  "Research Assistant, Examining Nutrition, Exercise, and Rest in Growing Youth (ENERGY) Lab",
  "Write, edit, and conduct statistical analyses for peer-reviewed manuscripts, utilizing structural equation modeling and approaches to categorical data analysis; Propose and manage new research projects; Write and conceptualize grant applications for relevant funding opportunities; Analyze data across different statistical platforms (e.g., R, Mplus, SAS); Work collaboratively on federally funded research projects; Directly mentor and supervise undergraduate research assistants on research projects, including assisting with student-led research projects; and Assist with administrative tasks.",
  "Aug. 2022--Present",
  "Supervisor: Jason Van Allen, Ph.D.",
  
  "Research Coordinator, Children's Television Project",
  "Supervise coders and research assistants working on a longitudinal research project; Work with PIs to implement and improve upon long-term project goals; Organize and manage data from the current season as well as from past years; Assign and track generation of character sheets, coding, cleaning, and collapsing; Generate and manage coder information surveys, training surveys, and coding instrument responses; Respond to student inquiries in a timely manner; and Assist in organizing structure of weekly class meetings as well as semester-long schedule.",
  "Aug. 2021--May 2022",
  "Supervisor: Calvin Gidney, Ph.D.",
  
    "Research Assistant, Tufts Pets and Well-Being Lab",
  "Work closely with research team on funded research projects; Assist with participant recruitment, consent, protocol training, data collection, debriefing, and tracking; Draft manuscripts and grant proposals; Conduct systematic literature reviews and analyses; Handle data entry and analysis; and Assist with administrative tasks.",
  "May 2021--Aug. 2022",
  "Supervisor: Megan K. Mueller, Ph.D.",
  
    "Research Assistant, Tufts Initiative for Human-Animal Interaction",
  "Draft manuscripts; Conduct qualitative interviews with participants; Provide general administrative assistance on a number of funded research projects; Work with the Tufts IRB to help ensure that all aspects of the research studies are in compliance with the applicable regulations and institutional guidelines prior to IRB approval; Facilitate feedback on key documents and managing a collaborative workspace with stakeholders; Oversee projects through varying phases of development; Prepare, draft, and finalize stakeholder and research group meeting agendas and minutes; and Draft and finalize site and study documents.",
  "Aug. 2019--Aug. 2022",
  "Supervisor: Deborah Linder, DVM, MS, DACVN",
) %>%
  detailed_entries(
    what = Role,
    when = Year,
    why = Research,
    where = Supervisor
  )
```

## Statistical Training

```{r}
tribble(
  ~Year, ~Organization, ~Desc,
"2024", "Instructor: Andrew K. Littlefield, Ph.D.", "Categorical Data Analysis (In Progress)",
"2023", "Instructor: Andrew K. Littlefield, Ph.D.", "Structural Equation Modeling for Psychologists",
"2023", "Instructor: Nicholas Croft Borgogna, Ph.D.", "Advanced Correlational Methods and Factor Analysis",
"2022", "Instructor: Martina I. Klein, Ph.D.", "Experimental Design",
) %>% 
  detailed_entries(
    what = Desc,
    when = Year, 
    where = Organization
  )
```

## Clinical Experience

```{r}
tribble(
  ~ Role,
  ~ Research,
  ~ Year,
  ~ Supervisor,
            "Texas Tech University, Texas Tech University Psychology Clinic",
  "Graduate Student | Individual Adult and Child Therapist",
  "Sep. 2023--Present",
  "Supervisors: Andrew K. Littlefield, Ph.D., Sarah E. Victor, Ph.D., John L. Cooley, Ph.D., Jason Van Allen, Ph.D., Adam T. Schmidt, Ph.D., Jonathan Singer, Ph.D.",
  "Texas Tech University, Texas Tech University Psychology Clinic",
  "Provide long-term, individual psychotherapy for anxiety disorders (e.g., generalized anxiety disorder, social anxiety disorder), mood disorders (e.g., major depressive disorder, persistent depressive disorder), chronic pain, attention-deficit/hyperactivity disorder, oppositional defiant disorder, and prolonged grief disorder.",
  "Sep. 2023--Present",
  "Supervisors: Andrew K. Littlefield, Ph.D., Sarah E. Victor, Ph.D., John L. Cooley, Ph.D., Jason Van Allen, Ph.D., Adam T. Schmidt, Ph.D., Jonathan Singer, Ph.D.",
                "Texas Tech University, Texas Tech University Psychology Clinic",
  "Receive didactic training in evidence-based treatment protocols, including Parent Management Training, Defiant Children, Trauma-Focused Cognitive Behavioral Therapy, and Motivational Interviewing.",
  "Sep. 2023--Present",
  "Supervisors: Andrew K. Littlefield, Ph.D., Sarah E. Victor, Ph.D., John L. Cooley, Ph.D., Jason Van Allen, Ph.D., Adam T. Schmidt, Ph.D., Jonathan Singer, Ph.D.",
                "Texas Tech University, Texas Tech University Psychology Clinic",
  "Implement evidence-based treatments and theoretically informed case conceptualization built on Cognitive Behavioral Therapy, Acceptance and Commitment Therapy, Behavioral Activation, and Motivational Interviewing",
  "Sep. 2023--Present",
  "Supervisors: Andrew K. Littlefield, Ph.D., Sarah E. Victor, Ph.D., John L. Cooley, Ph.D., Jason Van Allen, Ph.D., Adam T. Schmidt, Ph.D., Jonathan Singer, Ph.D.",
                  "Texas Tech University, Texas Tech University Psychology Clinic",
  "Utilize treatment protocols, including the \\textit{Unified Protocol for Transdiagnostic Treatment of Emotional Disorders}, \\textit{ACT Made Simple}, \\textit{Managing Chronic Pain: A Cognitive-Behavioral Therapy Approach}, and \\textit{Cognitive Behavioral Therapy for Insomnia in Veterans}.",
  "Sep. 2023--Present",
  "Supervisors: Andrew K. Littlefield, Ph.D., Sarah E. Victor, Ph.D., John L. Cooley, Ph.D., Jason Van Allen, Ph.D., Adam T. Schmidt, Ph.D., Jonathan Singer, Ph.D.",
                    "Texas Tech University, Texas Tech University Psychology Clinic",
  "Provide long-term individual and parent-based therapy for children utilizing treatment protocols, including \\textit{Defiant Children}, \\textit{A Clinical Guide to Pediatric Sleep}, and \\textit{Multidimensional Grief Therapy}.",
  "Sep. 2023--Present",
  "Supervisors: Andrew K. Littlefield, Ph.D., Sarah E. Victor, Ph.D., John L. Cooley, Ph.D., Jason Van Allen, Ph.D., Adam T. Schmidt, Ph.D., Jonathan Singer, Ph.D.",
                      "Texas Tech University, Texas Tech University Psychology Clinic",
  "Design visual aids, client worksheets, and homework documents for clients, consistent with evidence-based treatment protocols.",
  "Sep. 2023--Present",
  "Supervisors: Andrew K. Littlefield, Ph.D., Sarah E. Victor, Ph.D., John L. Cooley, Ph.D., Jason Van Allen, Ph.D., Adam T. Schmidt, Ph.D., Jonathan Singer, Ph.D.",
                          "Texas Tech University, Texas Tech University Psychology Clinic",
  "Assess for suicide and self-harm risk, create safety plans, monitor risk throughout treatment, assess for and report abuse and neglect to the appropriate safety organizations, and communicate safety-related concerns to parents and caregivers of children.",
  "Sep. 2023--Present",
  "Supervisors: Andrew K. Littlefield, Ph.D., Sarah E. Victor, Ph.D., John L. Cooley, Ph.D., Jason Van Allen, Ph.D., Adam T. Schmidt, Ph.D., Jonathan Singer, Ph.D.",
                            "Texas Tech University, Texas Tech University Psychology Clinic",
  "Advocate for clients in additional contexts, including medical settings and places of education.",
  "Sep. 2023--Present",
  "Supervisors: Andrew K. Littlefield, Ph.D., Sarah E. Victor, Ph.D., John L. Cooley, Ph.D., Jason Van Allen, Ph.D., Adam T. Schmidt, Ph.D., Jonathan Singer, Ph.D.",
                              "Texas Tech University, Texas Tech University Psychology Clinic",
  "Conduct psychodiagnostic evaluations (including structured and semi-structured interviews) and assessment batteries, and provide feedback to clients.",
  "Sep. 2023--Present",
  "Supervisors: Andrew K. Littlefield, Ph.D., Sarah E. Victor, Ph.D., John L. Cooley, Ph.D., Jason Van Allen, Ph.D., Adam T. Schmidt, Ph.D., Jonathan Singer, Ph.D.",
                                "Texas Tech University, Texas Tech University Psychology Clinic",
  "Write psychodiagnostic reports and treatment progress reports, including intake reports, treatment plans, and termination summaries.",
  "Sep. 2023--Present",
  "Supervisors: Andrew K. Littlefield, Ph.D., Sarah E. Victor, Ph.D., John L. Cooley, Ph.D., Jason Van Allen, Ph.D., Adam T. Schmidt, Ph.D., Jonathan Singer, Ph.D.",
  
            "University Medical Center (UMC) Health System, Pediatrics",
  "Practicum Student | Individual Therapist",
  "Sep. 2024--Present",
  "Supervisor: Jason Van Allen, Ph.D.",
        "University Medical Center (UMC) Health System, Pediatrics",
  "Provide a variety of psychological services offered within the Pediatric
Intensive Care Unit, the general Pediatrics Department, the Neonatal Intensive Care Unit, and
others.",
  "Sep. 2024--Present",
  "Supervisor: Jason Van Allen, Ph.D.",

            "Equine-Assisted Positively Fit",
  "Practicum Student | Individual Therapist",
  "Mar. 2024--Present",
  "Supervisor: Jason Van Allen, Ph.D.", 
              "Equine-Assisted Positively Fit",
  "Lead therapist providing a family-focused, weight management intervention to youth and their families.",
  "Mar. 2024--Present",
  "Supervisor: Jason Van Allen, Ph.D.",

  "Texas Tech University, Grief Therapy with Adolescents",
  "Practicum Student",
  "Sep. 2023--Aug. 2024",
  "Supervisor: Jonathan Singer, Ph.D.",
          "Texas Tech University, Grief Therapy with Adolescents",
  "Receive didactic training in \\textit{Trauma and Grief Component Therapy} for adolescents who have lost a family member.",
  "Sep. 2023--Aug. 2024",
  "Supervisor: Jonathan Singer, Ph.D.",
  
      "Texas Tech University, CBT Pain Program for Adolescents",
  "Practicum Student",
  "Sep. 2023--Aug. 2024",
  "Supervisor: Caroline Cummings, Ph.D.",
        "Texas Tech University, CBT Pain Program for Adolescents",
  "Receive didactic training in CBT-based pain protocols---\\textit{Children's Health and Illness Recovery Program} and \\textit{The Comfort Ability}---for adolescents with chronic pain and their parents.",
  "Sep. 2023--Aug. 2024",
  "Supervisor: Caroline Cummings, Ph.D.",
  
    "Texas Tech University, Texas Tech University Psychology Clinic",
  "Clinic Co-Director",
  "Jan. 2023--May 2023",
  "Supervisor: Megan A. Thoen, Ph.D.",
    "Texas Tech University, Texas Tech University Psychology Clinic",
  "Conduct first-contact intake screenings of incoming clients, including assessment and documentation of risk, history, and presenting concerns.",
  "Jan. 2023--May 2023",
  "Supervisor: Megan A. Thoen, Ph.D.",
) %>%
  detailed_entries(
    what = Role,
    when = Year,
    why = Research,
    where = Supervisor,
    .protect = FALSE
  )
```

# Teaching and Mentoring Experience

## Teaching

```{r}
tribble(
  ~ Course,
  ~ Instructor,
  ~ Semester,
  ~ Department,
  "Guest Lecturer, PSY 1300: General Psychology ",
  "Course Instructor: Carol Fadalla",
  "Fall 2024 ",
  "Texas Tech University, Department of Psychological Sciences ",
  
  "Guest Lecturer, PSY 1300: General Psychology",
  "Course Instructor: Brelynne Baldwin, M.A.",
  "Fall 2024",
  "Texas Tech University, Department of Psychological Sciences",
  
  "Teaching Assistant, PSY 2400: Statistical Methods Lab",
  "Course Instructor: Will Crescioni, Ph.D. | Average Student Rating: 4.5/5.0",
  "Fall 2022",
  "Texas Tech University, Department of Psychological Sciences",
  
  "Teaching Assistant, CSHD 0159: Understanding Child Development Through Film",
  "Course Instructor: Calvin Gidney, Ph.D.",
  "Fall 2020",
  "Tufts University, Eliot-Pearson Department of Child Study and Human Development",
  
  "Teaching Assistant, CH 0099: Special Topics In Community Health, One Health",
  "Course Instructor: Deborah Linder, DVM, MS, DACVN",
  "Fall 2020",
  "Tufts University, Department of Community Health",
) %>%
  detailed_entries(
    what = Course,
    when = Semester,
    where = Department,
    why = Instructor
  )
```

## Mentoring

```{r}
tribble(
  ~ Advisee,
  ~ Instructor,
  ~ Semester,
  "Fanny Arendt",
    "Current mentee",
    "2024--Present",
  "Cyerra Jones",
    "Current mentee",
    "2023--Present",
  "Madeleine Valley",
    "Current mentee",
    "2023--Present",
  "Amanda Tabansi",
    "Undergraduate Research Assistant",
    "2023--2024",
  "Macie Le",
    "Undergraduate Research Assistant",
    "2023--2023",
  "Abigail Woodall",
    "Subsequent Position: Student, Master of Science in Marriage & Family THerapy, Texas Woman's University",
    "2023--2024",
  "Sara Phy",
    "Subsequent Position: Student, Master of Public Health, Nutritional Sciences, Dietetics Concentration, University of Michigan",
    "2023",
  "Brooke Streicher",
    "Subsequent Position: Research Coordinator, Texas Tech University",
    "2022--2023",
  "Ellis Renwick-Archibold",
    "Science Research Program, New Rochelle High School",
    "Summer 2022",

) %>%
  detailed_entries(
    what = Advisee,
    when = Semester,
    why = Instructor
  )
```

# Editorial and Reviewing Experience

[Web of Science Profile](https://www.webofscience.com/wos/author/record/ABE-9213-2021)

## Ad hoc Reviewer

Translational Issues in Psychological Science

## Fellowship Reviewer

```{r}
tribble(
  ~Year, ~Organization, ~Desc,
"2024", "APAGS/Psi Chi Junior Scientist Fellowship", "Graduate Student Reviewer",
) %>% 
  detailed_entries(
    what = Desc,
    when = Year, 
    where = Organization
  )
```

# Professional Service and Development

## Service

```{r}
tribble(
  ~Year, ~Organization, ~Desc,
"2024", "SCCAP, Division 53", "Society of Clinical Child and Adolescent Psychology (SCCAP) Mentor",
"2022--2023", "American Psychological Association, Division 17, Section 13: The Section on Human-Animal Interaction: Research and Practice", "Inclusion, Diversity, Equity, and Access (IDEA) Committee Member",
"2022--2023", "American Psychological Association, Division 17, Section 13: The Section on Human-Animal Interaction: Research and Practice", "Student Representative",
  "2021--2023", "American Psychological Association", "APA Campus Ambassador",
) %>% 
  detailed_entries(
    what = Desc,
    when = Year, 
    where = Organization
  )
```
  
## Development

```{r}
tribble(
  ~Year, ~Organization, ~Desc,
"25 Jul. 2024", "Megan Renna, Ph.D.", "Dialectical Behavior Therapy (DBT) Seminar",
"7 Jun. 2024", "Compass Mental Health Training & Consultation", "Virtual BPD COMPASS Introductory Workshop",
"May 2024", "Texas A&M Health Telehealth Institute", "Telehealth 101",
"9 Nov. 2023", "The Trauma and Grief Center at the Hackett Center for Mental Health", "Multidimensional Grief Therapy (MGT) Overview Training",
"May 2023", "Texas Tech University", "The Groundwork Program",
"Mar. 2023", "Texas Tech University", "Organizing the Academic CV Workshop",
"Feb. 2023", "Texas Tech University", "Writing the Academic Cover Letter Workshop",
"Jan. 2023", "Texas Tech University", "Making Equitable Attendance Policies Workshop",
) %>% 
  detailed_entries(
    what = Desc,
    when = Year, 
    where = Organization
  )
```
  
# Skills

```{r}
tribble(
  ~Category, ~Desc,
  "Programming & Software:", "R, RStudio, Quarto, Markdown, MPlus, SAS, SPSS, MATLAB, REDCap, Qualtrics, LaTeX",
  "Languages:", "English--Native; German--Intermediate High (ACTFL); Spanish--Novice Mid (ACTFL)"
) %>% 
  brief_entries(
    what = Desc,
    when = Category
  )
```

# Certifications

```{r}
tribble(
  ~Year, ~Organization, ~Desc,
  "21 Sep. 2023", "MoCA Cognitive Assessment", "Certified Rater",
  "6 Apr. 2023", "QPR Institute", "QPR Gatekeeper",
  "6 Jan. 2023", "CITI Program", "Working with Dogs in Research Settings",
  "13 Dec. 2022", "CITI Program", "Working With Horses In An Agricultural Research Setting",
  "10 Sep. 2022", "CITI Program", "TTU Human Subject Research Course",
  "9 Sep. 2022", "CITI Program", "Social and Behavioral Responsible Scholarship Course",
) %>% 
  detailed_entries(
    what = Desc,
    when = Year, 
    where = Organization
  )
```

# Professional Society Affiliations  

```{r}
tribble(
  ~Desc,
  "American Psychological Association, Division 54: Society of Pediatric Psychology","APA Division 54: Sports Medicine and Orthopedics SIG","APA Division 54: Pediatric Research/Innovative Statistical Methodologies SIG", "APA Division 54: Gender Health SIG","APA Division 54: Diversity SIG","Psi Chi, The International Honor Society in Psychology", "American Psychological Association, Division 53: Society of Clinical Child and Adolescent Psychology", "American Psychological Association, Division 17, Section 13: The Section on Human-Animal Interaction: Research and Practice", "Human Animal Bond Association"
) %>% 
  brief_entries(
    when = Desc
  )
```